% !TEX root = ../foundations.tex

\section{Questions}

\begin{enumerate}

	\item Is $H^*_\Gamma(X)\cong H^*(X)$ when not finitely generated?

	\item Is the cap product $H^i_\Gamma(M)\otimes H_{i+j}^\Gamma(M)\to H^\Gamma_j(M)$ isomorphic to the singular co(homology) cap product when $H^*(X)$ is not finitely generated?

	\begin{comment}
		\item For a closed oriented $M^m$, is the Poincar\'e duality map $H^i_\Gamma(M)\to H_{m-i}^\Gamma(M)$ that takes a cochain to a chain simply by converting the co-orientation to an orientation (via our standard construction over oriented manifolds) isomorphic to the singular co(homology) cap product with the fundamental class via the isomorphisms of homology and cohomology groups we have developed.
	\end{comment}

	\item What can we say about geometric homology/cohomology with coefficients?

	\item Can we develop theories of relative geometric homology/cohomology?

	\item If we consider only compact objects in $C_\Gamma^*(M)$ is the resulting cohomology theory isomorphic to $H^*_c(M)$?

	\item If we allow objects in $C^*_\Gamma(M)$ to be noncompact but with proper maps to $M$, is the resulting homology theory isomorphic to the standard $H^\infty_*(M)$?

	\item Are the cup and cap products we obtain working with $H^*_c(M)$ and $H^\infty_*(M)$ isomorphic to the standard ones?

	\item Can we show that our convention for co-orientating fiber products is unique for some nice set of properties?

	\item Can we express the map $\Ext(H_{i-1}^\Gamma(M),\Z)\to H^i_\Gamma(M)$ of Theorem \ref{T: UCT} in terms of linking numbers?

\end{enumerate}